Solar Flares Across the Spectrum: Observations and Instrumentation

### 2025-04-11 main_thesis_file.tex
Local changes

% use "plain" for committee to read, or for printing single-spaced in general
\documentclass[keepsake]{hvdthesis}

@@

\author{Soumya Roy}
\title{Dynamics of the Lower Solar Atmosphere}
\department{Jawaharlal Nehru University, New Delhi, India}
\subject{}
\month{July}
\year{2024}
\advisor{Prof. Durgesh Tripathi}

@@

% include the dissertation acceptance form
\includepdf[pages={1}]{placeholder_dac.pdf}

@@

\newpage
	%% Abstract
\input{abstract.tex}
%\input{abstract_short.tex}
	%% Table of Contents
{\singlespace
\tableofcontents
}
\newpage
\clearpage

@@

\vspace*{\fill}
{\centerline {\em Dedicated to everyone who pushed me one step at a time,}} 
{\centerline {\em every time I was about to give up!}}
{\centerline {\em And to my younger self, who was brave enogh to embark on this journey...}}
%\vskip 1.5cm
%{\centerline {\em }}
\vspace*{\fill}

@@

\chapter[Introduction]{Introduction}\label{c:intro}
\input{./introduction/intro}
\clearpage
%
\chapter{Existing Solar Observations and Techniques: A bridge towards Solar Ultraviolet Imaging Telescope}\label{c:chap2}
\chaptermark{Solar Observatories and Analysis Techniques}
\input{./chapter2/ms.tex}
\clearpage
%
\chapter{Intital preparatory analysis for SUIT}\label{c:chap3}
\chaptermark{SUIT preparatory analysis}
\input{./chapter3/ms.tex}
\clearpage
%
\chapter{Forward modelling SUIT observations}\label{c:chap4}
\chaptermark{SUIT forward model}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter4/ms.tex}

%
\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap5}
\chaptermark{Solar flares Mg II}
\begin{quote}
{ ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{{\em The Evolution of the Ratio of \ion{Mg}{2} Intensities During Solar Flares, Roy, S., \& Tripathi, D. 2024, ApJ, 964, 106, doi:\href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}}.}
\end{quote}
\input{./chapter5/ms.tex}
\clearpage
%
\chapter{Estimating thermal energy of two Solar Flares}\label{c:chap6}
\chaptermark{Solar flare energy}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter6/ms.tex}
\clearpage
%
\chapter{First flares observed by {\suit}}\label{c:chap7}
\chaptermark{First Flares observed with SUIT}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter7/ms.tex}
\clearpage
%

\chapter{Echoes of the Solar Inferno: Summary and Future Prospects}\label{c:chap8}
\chaptermark{Outlook}
\input{./chapter8/ms.tex}
\clearpage

>>>>

% use "plain" for committee to read, or for printing single-spaced in general
\documentclass[plain]{hvdthesis}

@@

\author{Soumya Roy | {\lbng \*s*eoumYo ray}}
\title{Solar Flares Across the Spectrum: Observations and Instrumentation}
\department{Jawaharlal Nehru University, New Delhi, India}
\subject{}
\month{July}
\year{2024}
\advisor{Prof. Durgesh Tripathi}

@@

% include the dissertation acceptance form
% \includepdf[pages={1}]{placeholder_dac.pdf}

@@

\includepdf[pages={1,2,3}]{placeholder_dac.pdf}
\newpage
	%% Abstract
\input{abstract.tex}
%\input{abstract_short.tex}
	%% Table of Contents
{\singlespace
\tableofcontents
}
\newpage
\clearpage

@@

\vspace*{\fill}
{\centerline {\em Dedicated to everyone who pushed me one step at a time,}} 
{\centerline {\em every time I was about to give up!}}
{\centerline {\em And to my younger self, who was brave enough to embark on this journey...}}
%\vskip 1.5cm
%{\centerline {\em }}
\vspace*{\fill}

@@

\chapter[Introduction]{Introduction}\label{c:intro}
\input{./introduction/intro_2}
\clearpage
%
\chapter{Existing Solar Observations and Techniques: A bridge towards Solar Ultraviolet Imaging Telescope}\label{c:chap2}
\chaptermark{Solar Observatories and Analysis Techniques}
\input{./chapter2/chap2_2}
\clearpage
%
\chapter{Estimating thermal energy of two Solar Flares}\label{c:chap3}
\chaptermark{Solar flare energy}
%\begin{quote}
%{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
%{authors,
%{\em journal reference info}}
%\end{quote}
\input{./chapter3/chap3}
\clearpage

\chapter{Forward modelling SUIT observations}\label{c:chap4}
\chaptermark{SUIT forward model}
%\begin{quote}
%{\em ~~~~~~~This thesis chapter originally appeared in the literature as} 
%{authors,
%{\em journal reference info}}
%\end{quote}
\input{./chapter4/chap4}
%
\chapter{Intital preparatory analysis for SUIT}\label{c:chap5}

\chaptermark{SUIT preparatory analysis}
\begin{quote}
    { \em~~~~~~~This thesis chapter originally appeared in the literature as} \\
{{\em {\bf Photometric calibration and spectral validation of
the Solar Ultraviolet Imaging Telescope onboard
Aditya-L1}, Sarkar, J., Roy, S., Ramaprakash, A.N., et. al.,  2025,  J. Astron. Telesc. Instrum. Syst. 11(1), 014005 (2025), doi:\href{https://www.spiedigitallibrary.org/journals/Journal-of-Astronomical-Telescopes-Instruments-and-Systems/volume-11/issue-1/014005/Photometric-calibration-and-spectral-validation-of-the-Solar-Ultraviolet-Imaging/10.1117/1.JATIS.11.1.014005.short}{10.1117/1.JATIS.11.1.014005}.}
\end{quote}
\input{./chapter5/chap5}
\clearpage
%

%
\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap6}
\chaptermark{Solar flares Mg II}
\begin{quote}
{ ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{{\em {\bf The Evolution of the Ratio of \ion{Mg}{2} Intensities During Solar Flares}, Roy, S., \& Tripathi, D. 2024, ApJ, 964, 106, doi:\href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}}.}
\end{quote}
\input{./chapter6/chap6}
\clearpage
%
\chapter{First flares observed by {\suit}}\label{c:chap7}
\chaptermark{First flares}
%\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as}\\ 
{{\em {\bf Near- and Mid-ultraviolet Observations of X-6.3 Flare on 2024 February 22 Recorded by the Solar Ultraviolet Imaging Telescope on board Aditya-L1}, Roy, S., Tripathi, D., Padinhatteeri, S., \& Ramaprakash, A. N., et. al., 2024, ApJL, 981, L19, doi:\href{https://iopscience.iop.org/article/10.3847/2041-8213/adb0be}{10.3847/2041-8213/adb0be}}.}
%{authors,
%{\em journal reference info}}
%\end{quote}
\input{./chapter7/chap7_2}
\clearpage
%
%
\chapter{Echoes of the Solar Inferno: Summary and Future Prospects}\label{c:chap8}
\chaptermark{Summary \& Outlook}
\input{./Outlook/outlook_2}
\clearpage
%
\appendix
\chapter{Calculation of Oscillator strengths for the Mg~\Romannum{2}~k~\&~h lines}\label{c:a1}
\chaptermark{Oscilator Strength Calculation}
\input{./Appendix1/a1}
\clearpage

\chapter{Modifications of the cold thick target model}\label{c:a2}
\chaptermark{Kappa Distribution Fit}
\input{./Appendix1/a2}
\clearpage

### 2025-04-11 pub.tex
Local changes

%%%%%%%%%%%
\begin{itemize}
    \item Soumya Roy and Durgesh Tripathi, 2024, ApJ, 964, 106, doi: \href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}
\end{itemize}
%%%%%%%%%%%

@@

%%%%%%%%%%%
\begin{itemize}
    \item Roy, S., et al., "Solar Ultraviolet Imaging Telescope (SUIT) Handbook", ISRO Aditya-L1 mission
    \item Roy, S., et al., "Estimation of Effects of Space-craft Jitter on SUIT Imaging", ISRO Aditya-L1 mission
\end{itemize}
%%%%%%%%%%%

>>>>

%%%%%%%%%%%
\begin{itemize}
    \item ``Evolution of the Ratio of \ion{Mg}{2} Intensities during Solar Flares", {\bf Soumya Roy} and Durgesh Tripathi, 2024, ApJ, 964, 106, doi: \href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}\footnotemark[1]
    \item ``Near and Mid-ultraviolet Observations of X-6.3 Flare on 2024 February 22 Recorded by the Solar Ultraviolet Imaging Telescope on board Aditya-L1", {\bf Soumya Roy}, Durgesh, Tripathi, Sreejith, P, \& Ramaprakash, A. N., et. al., 2024, ApJL, 981, L19, doi:\href{https://iopscience.iop.org/article/10.3847/2041-8213/adb0be}{10.3847/2041-8213/adb0be}\footnotemark[1]
    \item ``Photometric Calibration \& Spectral Validation of the Solar Ultraviolet Imaging Telescope onboard Aditya-L1", Janmejoy Sarkar, {\bf Soumya Roy}, A. N. Ramaprakash,... 2024, J. Astron. Telesc. Instrum. Syst. 11(1), 014005 (2025), doi:\href{https://www.spiedigitallibrary.org/journals/Journal-of-Astronomical-Telescopes-Instruments-and-Systems/volume-11/issue-1/014005/Photometric-calibration-and-spectral-validation-of-the-Solar-Ultraviolet-Imaging/10.1117/1.JATIS.11.1.014005.short}{10.1117/1.JATIS.11.1.014005}\footnotemark[1]
    \item ``Science Filter Characterization of the Solar Ultraviolet Imaging Telescope (SUIT) on board Aditya-L1", Janmejoy Sarkar, Rushikesh Deogaonkar, Ravi Kesharwani, ... {\bf Soumya Roy},... 2024, Exp. Astron., 59, 3 (2025), doi: \href{https://doi.org/10.1007/s10686-024-09973-5}{10.1007/s10686-024-09973-5}
    \item ``Solar Ultraviolet Imaging Telescope on board Aditya-L1", Durgesh Tripathi, A. N. Ramaprakash, Sreejith P,... {\bf Soumya Roy},... 2025, Sol. Phys., 300, 30, \href{10.1007/s11207-025-02423-1}{10.1007/s11207-025-02423-1}\footnotemark[1]
    \item ``X-class flare on Dec 31, 2023, observed by the Solar Ultraviolet Imaging Telescope", {\bf Soumya Roy}, Durgesh Tripathi, Sreejith P, \& A. N. Ramaprakash, et. al., 2025, ApJL, 983, L6, \href{https://doi.org/10.3847/2041-8213/adc387}{10.3847/2041-8213/adc387}
    \item ``Test and Calibration of the Solar Ultraviolet
Imaging Telescope (SUIT) on board Aditya-L1", Janmejoy Sarkar, Nived V. N., {\bf Soumya Roy}, Rushikesh Deogaonkar et al., 2025, Accepted for publication in Sol. Phys.

\end{itemize}
%%%%%%%%%%%

\section*{Submitted Articles}

%%%%%%%%%%%
\begin{itemize}
    \item ``Evolution of thermal and cumulative non-thermal energy in solar flares", {\bf Soumya Roy}, Sophie Musset, Katharine K. Reeves, Durgesh Tripathi, Christopher S. Moore, 2024, Submitted to ApJ\footnotemark[1]{}\footnotetext{Part of this thesis}
    \item ``Forward Modeling Observations of the Solar Ultraviolet Imaging Telescope (SUIT) on board Aditya-L1", {\bf Soumya Roy}, L. S. Anusha, Durgesh Tripathi, et al. 2024, Submitted to ApJ\footnotemark[1]{}\footnotetext{Part of this thesis}
    %\item ``Critical Science Plan of the Solar Ultraviolet Imaging Telescope (SUIT) onboard Aditya-L1 mission", Durgesh Tripathi, A. N. Ramaprakash, ... {\bf Soumya Roy}, in Preparation
\end{itemize}
%%%%%%%%%%%

@@

%%%%%%%%%%%
\begin{itemize}
    \item Roy, S., et al., "Solar Ultraviolet Imaging Telescope (SUIT) Handbook", ISRO Aditya-L1 mission
    \item Roy, S., et al., "Estimation of Effects of Space-craft Jitter on SUIT Imaging", ISRO Aditya-L1 mission\footnotemark[1]{}
\end{itemize}
%%%%%%%%%%%
